---
title: "Portfolio 6"
---

For my final portfolio, I would like to do something special as a thank you to Dr. Mason for her hard work in putting this class together on such short notice, as well as guiding through the many hardships of coding. Specifically, I would like to use some of my personal skills as well as things I have learned from online research, to create a thank you message in R.

As learned at the beginning of the semester, always load the necessary packages:
```{r}
library(ggplot2)
```

I wanted to make this graph as glamorous as my knowledge on coding allows me, with little research from online sources. I decided to go for something of a "celebration gradient" representative of the completion of another semester, and to express my gratitude towards Prof. Mason effectively. here is the result:

```{r}
ggplot() +
  annotate("text", 0.5, 0.55,
           label = "Thank you",
           size = 14,
           color = "gold",
           fontface = "bold") +
  annotate("text", 0.5, 0.45,
           label = "Dr. Mason!",
           size = 16,
           color = "red",
           fontface = "bold") +
  theme_void() +
  xlim(0, 1) + ylim(0, 1) +
  theme(
    plot.background = element_rect(fill = "navy", color = NA)
  )
```
It may not be the greatest looking, but I hope that it is sufficient enough to brighten your day a little bit. Thank you for your hard work Prof. Mason, and I wish you the best of luck from now onwards. I will definitely make sure to reach out to you if I have any other coding questions for future classes. Thanks again!
